%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cameron Williams          %
% ECE 351-51                %
% Lab Number 1              %
% 28 January 2020           %
% Instructor Philip Hagen   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}

% Language and font encoding
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{appendix}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{gensymb}
\usepackage{amssymb}
\usepackage[final]{pdfpages}

% Sets page size and margins
\usepackage[a4paper, margin=1in]{geometry}

%Line Spacing
\setstretch{1.5}

%-------------------Begin Editing Here---------------------
%Info for Title Page
\title{Introduction to Python 3.x and LaTeX}
\author{Cameron Williams\\ECE 351-51\\Lab Report 1}
\date{28 January 2020}
\begin{document}

%Make a Title Page
\vspace{\fill}
\maketitle
\vspace{\fill}
\clearpage

\newpage
%Part 1 Summary
\section{Part 1 Summary}
    \par Following the lab instructions that were provided, I read the documentation that was linked. Then I took a look at the Spyder keyboard shortcuts. I found a werid shortuct that uses the "meta" key and 'Y' to "Yank". I saved a new python script in Spyder as "Williams\_Cameron\_ECE351\_Lab1.py".
\section{Part 2 Summary}
    \par Most of this part went pretty smoothly, but I had some difficulty with getting the single quotes to show up inside of the string, so I changed the code slightly to achieve the output shown in the lab handout. I also ran into a small snag with aliasing. It seemed like under certain conditions a section being run by itself must have aliases for package names declared in the section, otherwise it won't recognize the alias.
\section{Part 3 Summary}
    \par I had already used LaTeX for a course before, so was already reasonably familiar with it. However, I expect the LaTeX "cheat sheet" provided will be very useful throughout the course.
\newpage
%Questions
\section*{Questions}

\begin{enumerate}
    \item Which course are you most excited for in your degree? Which course have you enjoyed the most so far?
\end{enumerate}
    \par I am excited to get further into the Digital Design class that I am taking this semester since I'm really interested in working with FPGAs. So far, I enjoyed Microcontrollers the most.
\begin{enumerate}[resume]
    \item Leave any feedback on the clarity of the expectations, instructions, and deliverables.
\end{enumerate}
    \par I think the expectations expressed this far into the course has been clear and I look foward to getting better with Python.
    
\end{document}